---
title: "Data Wrangling"
author: "Freya Maghani"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data type Trasformation and Missing Value Imputation

As part of data cleaning , some columns in the dataset must have their formats changed and the missing and unrelated values are replaced with NA.

The data type of Education and Marital Status are categorical and the format is changed from Char to factor.
The date column's data type is changed to date type, using **library(lubridate)**.
The missing values are replaced, utilizing **library(stringr)** in the process.

```{r Data wrangling , retreiving columns' values and types and changing the format}

setwd("C:/IS/5250-Visual Analytics/Rproject/Dataset")
sales_campaign_final<- read.csv("sales_campaign_final.csv", header=TRUE)

dim(sales_campaign_final)
summary(sales_campaign_final)

sales_campaign_final$Education<-as.factor(sales_campaign_final$Education)
unique(sales_campaign_final$Education)
sales_campaign_final$Marital_Status<-as.factor(sales_campaign_final$Marital_Status)
unique(sales_campaign_final$Marital_Status)

library(lubridate)
head(sales_campaign_final$Dt_Customer)
sales_campaign_final$Dt_Customer<-dmy(sales_campaign_final$Dt_Customer)
summary(sales_campaign_final)

class(sales_campaign_final$Dt_Customer)
class(sales_campaign_final$Education)
class(sales_campaign_final$Marital_Status)

```


```{r Data wrangling , Replacing the missing/irrevant values with NA, Removing the rows with NA values}

unique(sales_campaign_final$Marital_Status)
   

library(stringr)
absurd<- which(str_detect(sales_campaign_final$Marital_Status, "Absurd"))
Alone<- which(str_detect(sales_campaign_final$Marital_Status, "Alone"))
YOLO<- which(str_detect(sales_campaign_final$Marital_Status, "YOLO"))

sales_campaign_final$Marital_Status[absurd]<- NA
sales_campaign_final$Marital_Status[Alone]<- NA
sales_campaign_final$Marital_Status[YOLO]<- NA
unique(sales_campaign_final$Marital_Status)

sales_campaign_final$Marital_Status <- as.factor(sales_campaign_final$Marital_Status)
missing_Marital_Status<-which(is.na(sales_campaign_final$Marital_Status))
sales_campaign_final <- sales_campaign_final[-missing_Marital_Status,]

summary(sales_campaign_final)
unique(sales_campaign_final$Marital_Status)

write.csv(sales_campaign_final,file="sales_campaign_final.csv")
```
